Proposed Solution

### 2016-01-29 motiv1.tex
fixing up motiv examples

When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
 \texttt{
 \hspace*{3em}extension = mysql.so\\
 \hspace*{3em}...\\
 \hspace*{3em}extension = recode.so}\\
This file caused that the Apache server could not start due to 
the segmentation fault error. Running \app on this file would return\\
 \texttt{
ORDERING ERROR: Expected "extension"recode.so" BEFORE "extension""mysql.so"
  }\\
Indeed, this was the source of the error. When using PHP in Apache, the
extension ``mysql.so'' depends on ``recode.so'' and the relative ordering 
of two of them is crucial. The user is informed that ``recode.so'' should appear before ``mysql.so''.

@@

If the user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:\\
\texttt{
 \hspace*{3em}overlay ppolicy\\}
However, this configuration file will make LDAP server fail to work.
Running \app on this configuration file would return:
MISSING KEYWORD ERROR: Expected "overlay""ppolicy" in the same file as: "include""schema/ppolicy.schema"\\
This was the source of the error. When using the password policy overlay
in OpenLDAP, we have to first include the related schema. The correct configuration should be:\\
\texttt{
 \hspace*{3em}include schema/ppolicy.schema\\
 \hspace*{3em}overlay ppolicy\\
}

@@

If the user tries to install MySQL, she first needs to 
initiate the path for the
log information generated by MySQL. A user puts the following code in 
her MySQL configuration file:\\
\texttt{
 \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
After \app analyzed this configuration file, it correctly identifies the error:
\begin{verbatim}
TYPE ERROR: Expected a Int with P=1.0  for "general_log[mysqld]"
\end{verbatim}
The entry ``general\_log'' should be an integer, 
and not a string. In MySQL, there is another entry named
``general\_log\_file'' which is used to specify the log path.

@@

When configuring PHP on MySQL, the user writes the following lines 
of entries in her both PHP and MySQL configuration files:\\
\texttt{
 \hspace*{3em}mysql's config\\
 \hspace*{3em}max\_connections = 300\\
 \hspace*{3em}...\\
 \hspace*{3em}php's config\\
 \hspace*{3em}mysql.max\_persistent = 400\\}
This will cause MySQL to abort with the error information:
``too many connections''.
Running \app on this combined configuration file returns:
INTEGER RELATION ERROR: Expected "max\_connections">="mysql.max\_persistent"
\\
We are successfully able to derive arithmetic relations between integer values.
In particular, the ``mysql.max\_persistent'' in PHP should be no
larger than the ``max\_connections'' in MySQL configuration file.

>>>>

When configuring PHP to run with the Apache HTTP Server the user writes, among others, the following lines:\\
 \texttt{
 \hspace*{3em}extension = mysql.so\\
 \hspace*{3em}...\\
 \hspace*{3em}extension = recode.so}\\
This file caused the Apache server to fail to start due to a segmentation fault error.
When using PHP in Apache, the extension ``mysql.so'' depends on ``recode.so'' and the relative ordering of two of them is crucial. 
The user is informed that ``recode.so'' should appear before ``mysql.so''.
 Running \app on this file would return\\
 \texttt{
ORDERING ERROR: Expected "extension"recode.so" BEFORE "extension""mysql.so"
  }\\

@@

If the user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:\\
\texttt{
 \hspace*{3em}overlay ppolicy\\}
However, this configuration file will make LDAP server fail to work.
Running \app on this configuration file would return:
MISSING KEYWORD ERROR: Expected "overlay""ppolicy" in the same file as: "include""schema/ppolicy.schema"\\
When using the password policy overlay in OpenLDAP, we have to first include the related schema. The correct configuration should be:\\
\texttt{
 \hspace*{3em}include schema/ppolicy.schema\\
 \hspace*{3em}overlay ppolicy\\
}

@@

If the user tries to install MySQL, she first needs to 
initiate the path for the
log information generated by MySQL. A user puts the following code in 
her MySQL configuration file:\\
\texttt{
 \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
The entry ``general\_log'' should be an integer, 
and not a string. In MySQL, there is another entry named
``general\_log\_file'' which is used to specify the log path.  
After \app analyzed this configuration file, it correctly identifies the error:
\begin{verbatim}
TYPE ERROR: Expected a Int with P=1.0  for "general_log[mysqld]"
\end{verbatim}

@@

When configuring PHP on MySQL, the user writes the following lines 
of entries in her both PHP and MySQL configuration files:\\
\texttt{
 \hspace*{3em}mysql's config\\
 \hspace*{3em}max\_connections = 300\\
 \hspace*{3em}...\\
 \hspace*{3em}php's config\\
 \hspace*{3em}mysql.max\_persistent = 400\\}
This will cause MySQL to abort with the error information:
``too many connections''.
We are successfully able to derive arithmetic relations between integer values.
In particular, the ``mysql.max\_persistent'' in PHP should be no
larger than the ``max\_connections'' in MySQL configuration file.
Running \app on this combined configuration file returns:
INTEGER RELATION ERROR: Expected "max\_connections">="mysql.max\_persistent"
\\
